Supporting Information:\\ Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-08-20 Manuscript/manuscriptPSsuppl.tex
Change manuscript to the ACS format

\documentclass[journal=jctcce]{achemso}

@@

\author{Hanne Antila}
\affiliation{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\author{Pavel Buslaev}
\affiliation{Moscow Institute of Physics and Technology, Dolgoprudny, Russia}
\author{Fernando Favela-Rosales}
\affiliation{Departamento de Investigaci\'{o}n, Tecnol\'{o}gico Nacional de M\'{e}xico, Campus Zacatecas Occidente, M\'{e}xico}
\author{Tiago M. Ferreira}
\affiliation{Halle, Germany}
\author{Ivan Gushchin}
\affiliation{Moscow Institute of Physics and Technology, Dolgoprudny, Russia}
\author{Matti Javanainen}
\affiliation{Institute of Organic Chemistry and Biochemistry of the 
Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2, CZ-16610 Prague 6, Czech Republic}
\author{Batuhan Kav}
\affiliation{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\author{Jesper J. Madsen}
\affiliation{Department of Chemistry, The University of Chicago, Chicago, Illinois, United States of America}
\affiliation{Department of Global Health, College of Public Health, University of South Florida, Tampa, Florida, United States of America}
\author{Josef Melcr}
\affiliation{Institute of Organic Chemistry and Biochemistry of the 
Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2, CZ-16610 Prague 6, Czech Republic}
\author{Markus Miettinen}
\affiliation{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\author{Ricky Nencini}
\affiliation{Institute of Organic Chemistry and Biochemistry of the 
Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2, CZ-16610 Prague 6, Czech Republic}
\author{O. H. Samuli Ollila}
\email{samuli.ollila@helsinki.fi}
%\homepage[]{Your web page}
\affiliation{Institute of Organic Chemistry and Biochemistry of the 
Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2, CZ-16610 Prague 6, Czech Republic}
\affiliation{Institute of Biotechnology, University of Helsinki}
\author{Thomas J. Piggot}
\affiliation{Chemistry, University of Southampton, Highfield, Southampton SO17 1BJ, U.K}

@@

\clearpage
\section{Details of the rough subjective force field ranking (Fig.~\ref{comparisonTablePS})}

\section{Details of the force field ranking (Fig.~\ref{comparisonTablePS})}\label{Ranking} 
In Figure~\ref{HGorderParametersPS}) of main text we present a rough and subjective ranking of the force fields investigated in this work. 
The assessment was based on the data presented in Fig.~\ref{HGorderParametersPS}.
%
For each carbon (the columns in Fig.~\ref{HGorderParametersPS}),
we first investigated separately how well a given force field represents the {\bf magnitude} of the order parameters and their {\bf forking}.

>>>>

\documentclass[journal=jpcbfk,manuscript=article]{achemso}

@@

\author{Hanne Antila}
\affiliation{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\author{Pavel Buslaev}
\affiliation{Moscow Institute of Physics and Technology, Dolgoprudny, Russia}
\author{Fernando Favela-Rosales}
\affiliation{Departamento de Investigaci\'{o}n, Tecnol\'{o}gico Nacional de M\'{e}xico, Campus Zacatecas Occidente, M\'{e}xico}
\author{Tiago M. Ferreira}
\affiliation{NMR group - Institute for Physics, Martin-Luther University Halle-Wittenberg}
\author{Ivan Gushchin}
\affiliation{Moscow Institute of Physics and Technology, Dolgoprudny, Russia}
\author{Matti Javanainen}
\affiliation{Institute of Organic Chemistry and Biochemistry of the 
Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2, CZ-16610 Prague 6, Czech Republic}
\author{Batuhan Kav}
\affiliation{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\author{Jesper J. Madsen}
\affiliation{Department of Chemistry, The University of Chicago, Chicago, Illinois, United States of America}
\affiliation{Department of Global Health, College of Public Health, University of South Florida, Tampa, Florida, United States of America}
\author{Josef Melcr}
\affiliation{Institute of Organic Chemistry and Biochemistry of the 
Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2, CZ-16610 Prague 6, Czech Republic}
\author{Markus Miettinen}
\affiliation{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\author{Ricky Nencini}
\affiliation{Institute of Organic Chemistry and Biochemistry of the 
Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2, CZ-16610 Prague 6, Czech Republic}
\author{O. H. Samuli Ollila}
\email{samuli.ollila@helsinki.fi}
%%\homepage[]{Your web page}
\affiliation{Institute of Organic Chemistry and Biochemistry of the 
Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2, CZ-16610 Prague 6, Czech Republic}
\affiliation{Institute of Biotechnology, University of Helsinki}
\author{Thomas J. Piggot}
\affiliation{Chemistry, University of Southampton, Highfield, Southampton SO17 1BJ, U.K}

@@

\clearpage
%\section{Details of the rough subjective force field ranking (Fig.~\ref{comparisonTablePS})}

\section{Details of the force field ranking (Fig.~\ref{comparisonTablePS})}\label{Ranking} 
In Figure~\ref{comparisonTablePS} of main text we present a rough and subjective ranking of the force fields investigated in this work. 
The assessment was based on the data presented in Fig.~\ref{HGorderParametersPS}.
%
For each carbon (the columns in Fig.~\ref{HGorderParametersPS}),
we first investigated separately how well a given force field represents the {\bf magnitude} of the order parameters and their {\bf forking}.
